\textsf{Are large language models superhuman chemists?}

### 2024-10-25 src/tex/appendix.tex
remove unused text and reorder figures and tables according to Martino's suggestion
feat: add Nawaf's section
co-authored-by: n0w0f <pvt.nawaf@gmail.com>

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\textwidth]{figures/correlation_plot_is_number_nmr_peaks_complexity.pdf}
    \caption{\textbf{Dependence of the mean absolute error in predicting the number of NMR signals on the Böttcher complexity of the molecules.} The complexity measure proposed by \textcite{B_ttcher_2016} is an information-theoretic additive measure of compound complexity that follows chemical intuitions.
    The plot shows that for the \glspl{llm}, the predictive performance (measured as the mean absolute error in the prediction of the number of \gls{nmr} signals) is not correlated with the complexity of the molecules (that is, molecules tend to not to be able to predict the number of \gls{nmr} signals irregardless of molecular complexity). For inference based on reasoning, one would expect that the complexity of the molecule is a good predictor of the difficulty of the question.}
    \script{correlate_with_molecule_features.py}
    \label{fig:correlation_plot_is_number_nmr_peaks_complexity}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_score_distribution.pdf}
    \script{plot_human_score_distribution.py}
    \caption{\textbf{Distribution of human scores.} The histogram and kernel density estimates show the fraction of questions answered correctly by the human volunteers.
    Since the best possible score for each question is one and the worst possible score is zero, the values on this plot are between zero and one. A score of one would mean that a volunteer answered all questions correctly. A score of zero would mean that no question was answered correctly.
    We find that the scores for the questions that the human volunteers answered with tools are generally lower than the scores for the questions that the human volunteers answered without tools.
    }
    \label{fig:human_score_distribution}
\end{figure}

>>>>

\subsubsection{Curation workflow}
Questions were added via pull requests to the \chembench repository on GitHub.
This allowed for a manual review of each question by expert reviewers (with backgrounds in chemistry, materials science, chemical engineering, and physics).
The reviews were conducted directly on the GitHub platform, where our entire curation history is also publicly available.

The general guidelines followed by the reviewer are the following:

\begin{itemize}
    \item \textbf{Originality:} Questions should not be readily findable online or in other easily accessible sources (example \url{https://github.com/lamalab-org/chem-bench/pull/392#discussion_r1694299474})
    \item \textbf{Ambiguity:} Questions with unclear wording or multiple interpretations (example \url{https://github.com/lamalab-org/chem-bench/pull/420#discussion_r1698147159} )
    \item \textbf{Factual or heuristic Errors: }Questions containing factual inaccuracies or misconceptions are not included (example \url{https://github.com/lamalab-org/chem-bench/pull/389#discussion_r1686187301})
    \item \textbf{Out of Scope:} Questions outside the realm of chemistry are rejected.
    \item \textbf{Clarity and Difficulty: } They should pose a challenge and encourage exploration within the chemical domain.
    \item \textbf{Contribution to Dataset Diversity: }Questions should cover a wide range of chemical concepts and sub-disciplines. They should add value by expanding the breadth of the dataset. That is, questions already multiple (>10) times in the corpus in a similar form are rejected.
\end{itemize}

Reviewers also solved the questions to verify the answers. They also performed web searches to ensure questions were not easily found online. The reviewers often guided the revision process to ensure the question aligned with the guidelines. Questions that don't meet the criteria are either rejected or suggested for revision and most often, they are modified to a new question. Reviewers also provide feedback on the skill and difficulty annotations.

In addition to the manual review, we also performed automated checks to ensure the quality of the questions. The schemas, Latex templating, and other formatting aspects are checked automatically using GitHub Actions.

\subsubsection{Composition}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\textwidth]{figures/correlation_plot_is_number_nmr_peaks_complexity.pdf}
    \caption{\textbf{Dependence of the mean absolute error in predicting the number of NMR signals on the Böttcher complexity of the molecules.} The complexity measure proposed by \textcite{B_ttcher_2016} is an information-theoretic additive measure of compound complexity that follows chemical intuitions.
    The plot shows that for the \glspl{llm}, the predictive performance (measured as the mean absolute error in the prediction of the number of NMR signals) is not correlated with the complexity of the molecules. For inference based on reasoning, one would expect that the complexity of the molecule is a good predictor of the difficulty of the question.}
    \script{correlate_with_molecule_features.py}
    \label{fig:correlation_plot_is_number_nmr_peaks_complexity}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_score_distribution.pdf}
    \script{plot_human_score_distribution.py}
    \caption{\textbf{Distribution of human scores.} The histogram and kernel density estimates show the fraction of questions answered correctly by the human volunteers.
    Since the best possible score for each question is one and the worst possible score is zero, the values on this plot are between zero and one. A score of one would mean that a volunteer answered all questions correctly. A score of zero would mean that no question was answered correctly.}
    \label{fig:human_score_distribution}
\end{figure}
